Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-08 longSC.tex
correct for the references of freeze-out

The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_8}.
In case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_loworder} and show very weak $p_{\rm T}$ dependence for all centralities.
The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40-50\% centrality range where the data shows stronger $p_{\rm T}$ dependence than the models. The difference between the model calculations with the two parameterizations is very small. 
As for NSC(4,2), the model calculations overestimate the magnitude in the 5-20\% centrality range and underestimate in the centrality range $>$20\%. However the $p_{\rm T}$ dependence is well described by the model calculations in all centralities. 
While the difference of the model calculations between two parameterizations in most of the centrality ranges is rather small, the clear separation between two parameterizations are observed in 10-20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.

This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out as predicted in ~\cite{Luzum:2010ad}.
The comparisons to hydrodynamic models can further help to understand the viscous corrections to the momentum distributions at hadronic freeze-out~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
%\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}

>>>>

The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_8}.
In case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_loworder} and show very weak $p_{\rm T}$ dependence for all centralities.
The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40-50\% where the data shows stronger $p_{\rm T}$ dependence than the models. The difference between the model calculations with the two parameterizations is very small. 
As for NSC(4,2), the model calculations overestimate the magnitude in the 5-20\% centralities and underestimate in the centrality range $>$20\%. However the $p_{\rm T}$ dependence is well described by the model calculations in all centralities. 
While the difference of the model calculations between two parameterizations in most centralities is rather small, the clear separation between two parameterizations are observed in 10-20\% where both the magnitude and $p_{\rm T}$ dependence are different.

This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out as predicted in ~\cite{Niemi:2012aj}.
The comparisons to hydrodynamic models can further help to understand the viscous corrections to the momentum distributions at hadronic freeze-out~\cite{Dusling:2009df,Luzum:2010ad,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
%\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}
